 Allocation scoring rules as a generalization of quantile scoring rules

### 2023-05-19 notes/allocation_notes.rmd
a few lambda discussion edits

As a separable problem, this is amenable to being solved via its dual (see [@ruszczynski2011nonlinear], section 4.4). With the Lagrangian
\begin{align}
L(\mathbf{x}, \lambda; K) = \sum_{i=1}^{N} \sbar_{F_i}(x_i) + \lambda \left(\sum_{i=1}^{N}w_i x_i - K\right) \label{Lagrangian}
\end{align}
we have the dual problem of maximizing over $\lambda \geq 0$ the objective function
\begin{align}
L_D(\lambda; K) &= \min_{0 \leq \mathbf{x}} L(\mathbf{x}, \lambda) = 
-\lambda K + \sum_{i=1}^{N} \underset{0 \leq x_i}{\min} \left\{\lambda w_i x_i + \sbar_{F,i}(x_i)\right\} \label{dual_eq}
\end{align}
which gives lower bounds on $\sbar_F(\mathbf{x}^{\star})$ at a solution $\mathbf{x}^{\star}$ to the primal AP. In particular, when $O_i>0$ for all $i$, $L_D(0)$ gives the total score $\sbar_F(\mathbf{q}_{\symbfit{\alpha}, F})$ when the constraint does not prevent the forecaster from giving the quantiles in each component. When the constraint is active, the forecaster will generally not be able to attain a total score this low and the greatest lower bound on their score will correspond the maximizer $\lambda^{\star} = \lambda^{\star}(K)$ of \eqref{dual_eq}.

>>>>

As a separable problem, this is amenable to being solved via its dual (see [@ruszczynski2011nonlinear], section 4.4). With the Lagrangian
\begin{align}
L(\mathbf{x}, \lambda; K) = \sum_{i=1}^{N} \sbar_{F_i}(x_i) + \lambda \left(\sum_{i=1}^{N}w_i x_i - K\right) \label{Lagrangian}
\end{align}
we have the dual problem of maximizing over $\lambda \geq 0$ the objective function
\begin{align}
L_D(\lambda; K) &= \min_{0 \leq \mathbf{x}} L(\mathbf{x}, \lambda) = 
-\lambda K + \sum_{i=1}^{N} \underset{0 \leq x_i}{\min} \left\{\lambda w_i x_i + \sbar_{F,i}(x_i)\right\} \label{dual_eq}
\end{align}
which gives lower bounds on $\sbar_F(\mathbf{x}^{\star})$ at a solution $\mathbf{x}^{\star}$ to the primal AP. In particular, when $O_i>0$ for all $i$, $L_D(0; K)$ gives the total score $\sbar_F(\mathbf{q}_{\symbfit{\alpha}, F})$ when the constraint does not prevent the forecaster from giving the quantiles in each component. 
When the constraint is active, the forecaster will generally not be able to attain a total score this low and the greatest lower bound on their score will
 be $L_D(\lambda^{\star}; K)$ where $\lambda^{\star} = \lambda^{\star}(K)$ is the maximizer of \eqref{dual_eq}.
